Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
centering, wording
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60874 72bbbca6-d526-0410-a7d9-f06f51895060

	\begin{subfigure}[b]{0.3\textwidth}
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				көрші \& елдер \\
				\gmk{n.attr} \& \gmk{n.pl.nom} \\
				\gloss{neighbour} \& \gloss{countries} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{compound}}
		\end{dependency}
		\caption{Compounding: a nominal depending on an attributive nominal.}\label{fig:compound}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.3\textwidth}
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				әлем \& чемпионаты \\
				\gmk{n.nom} \& \gmk{n.px3sg.nom} \\
				\gloss{world} \& \gloss{championship} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{nmod}}
		\end{dependency}
		\caption{Indefinite genitive: A nominal depending on an indefinite genitive.}\label{fig:indefgen}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.3\textwidth}
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				Иранның \& экономиясы \\
				\gmk{n.gen} \& \gmk{n.px3sg.nom} \\
				\gloss{Iran's} \& \gloss{economy} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{nmod}}
		\end{dependency}
		\caption{Definite genitive: A nominal depending on an definite genitive.}\label{fig:indefgen}
	\end{subfigure}

>>>>

	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				көрші \& елдер \\
				\gmk{n.attr} \& \gmk{n.pl.nom} \\
				\gloss{neighbour} \& \gloss{countries} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{compound}}
		\end{dependency}
		\caption{Compounding: an attributive nominal depending on a nominal.}\label{fig:compound}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				әлем \& чемпионаты \\
				\gmk{n.nom} \& \gmk{n.px3sg.nom} \\
				\gloss{world} \& \gloss{championship} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{nmod}}
		\end{dependency}
		\caption{Indefinite genitive: An indefinite genitive depending on a nominal.}\label{fig:indefgen}
	\end{subfigure}
	\quad
	\begin{subfigure}[b]{0.3\textwidth}
		\centering
		\begin{dependency}[theme = simple, font = \small]
		   \begin{deptext}[column sep=0.3cm]
				Иранның \& экономиясы \\
				\gmk{n.gen} \& \gmk{n.px3sg.nom} \\
				\gloss{Iran's} \& \gloss{economy} \\
			\end{deptext}
			\depedge{1}{2}{\udlabel{nmod}}
		\end{dependency}
		\caption{Definite genitive: A definite genitive depending on a nominal.}\label{fig:defgen}
	\end{subfigure}
